Higher-Order unification for free!

### 2024-04-15 paper/main.tex
solve 1 todo

In order to make \Uo higher-order, we need to
take care of terms in \maybebeta.
In the example below, we can see that the basic compilation given in 
the previous section is not able to make the \Ho unification problem succeeds.
%
% make test ONLY=7006 TEX=tex
\printAlll
  {{{\lambda x.(f\appsep (X\appsep x)\appsep a),\lambda x.(f\appsep x\appsep a)}}}
  {{{\lambda x.(f\appsep (A\appsep x)\appsep a),\lambda x.(f\appsep x\appsep a)}}}
  {{{X,A,0}}}
  {{}}
\todo{fix indentation}
The unification problem $\hoUnifPb_1$ fails while trying to unify
$A \appsep x$ and $x$, which is equivalent to \elpiIn{app [uva A [], x]}
versus \elpiIn{x}.
In order to exploit the higher-order unification algorithm of the meta language,
we need to compile the \Fo{} term $X\appsep x$ into the \Ho term $A_x$,
which is \elpiIn{uva A [x]}.

>>>>

In order to make \Uo higher-order, we need to
take care of terms in \maybebeta.
In the example below, we can see that the basic compilation given in 
the previous section is not able to make the \Ho unification problem succeeds.
%
% make test ONLY=7006 TEX=tex
\printAlllSingle
  {{{\lambda x.(f\appsep (X\appsep x)\appsep a),\lambda x.(f\appsep x\appsep a)}}}
  {{{\lambda x.(f\appsep (A\appsep x)\appsep a),\lambda x.(f\appsep x\appsep a)}}}
  {{{X,A,0}}}
  {{}}
The unification problem $\hoUnifPb_1$ fails while trying to unify
$A \appsep x$ and $x$, which is equivalent to \elpiIn{app [uva A [], x]}
versus \elpiIn{x}.
In order to exploit the higher-order unification algorithm of the meta language,
we need to compile the \Fo{} term $X\appsep x$ into the \Ho term $A_x$,
which is \elpiIn{uva A [x]}.
